Codes for exploratory analysis

### 2025-05-03 code/eda-code/eda.qmd
Update eda.qmd

#making a reusable plotting function
create_trend_plot <- function(data, indicator_name, plot_title, y_label, color) {
  data %>%
    filter(indicator == indicator_name) %>%
    ggplot(aes(x = year, y = avg_value)) +
    geom_line(color = color, linewidth = 1) +
    geom_point(color = color, size = 2) +
    labs(title = plot_title, y = y_label, x = NULL) +
    theme_minimal(base_size = 12) +
    theme(plot.title = element_text(size = 11))
}

@@

#combining plots ----
#create a 3-column layout 
combined_plot <- wrap_plots(plots, ncol = 3) +
  plot_annotation(
    title = "Trends in Key Development Indicators",
    subtitle = "Country averages across time",
    caption = "Source: World Development Indicators",
    theme = theme(
      plot.title = element_text(size = 16, face = "bold"),
      plot.subtitle = element_text(size = 12)
    )
  )

#saving the plot
ggsave(
  filename = here::here("results", "figures", "development_indicators_trends.png"),
  plot = combined_plot,
  width = 16,
  height = 14,
  dpi = 300
)

>>>>

#making a reusable plotting function
create_trend_plot <- function(data, indicator_name, plot_title, y_label, color) {
  data %>%
    filter(indicator == indicator_name) %>%
    ggplot(aes(x = year, y = avg_value)) +
    geom_line(color = color, linewidth = 1) +
    geom_point(color = color, size = 2) +
    labs(title = plot_title, y = y_label, x = NULL) +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18))
}

@@

combined_plot <- wrap_plots(plots, ncol = 3) +
  plot_annotation(
    title = "Trends in Key Development Indicators",
    subtitle = "(The x-axis is labeled at the top of each plot, y-axis is labeled at the left side )",
    caption = "Source: World Development Indicators",
    theme = theme(
      plot.title = element_text(size = 19, face = "bold", hjust = 0.5),  # Center title
      plot.subtitle = element_text(size = 17, hjust = 0.5),              # Center subtitle
      plot.caption = element_text(size = 14)                         
    )
  )

#saving the plot
ggsave(
  filename = here::here("results", "figures", "development_indicators_trends.png"),
  plot = combined_plot,
  width = 16,
  height = 18,
  dpi = 300
)
